---
title       : Estimating MPG
subtitle    : Developing Data Products Assignment
author      : Joanna Chan
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Introduction
Estimating MPG using dataset 'mtcars' from R library. 
This dataset comprises fuel consumption of 32 cars based on 10 factors.

A step-wise approach was used to identify the significant 
factors affecting MPG. The identified significant factors are:

1. Number of cylinder
2. Horsepower
3. Weight

---
## Modeling
The multivariate linear model below shows the coefficients of 
the significant factors:
```{r mod, results='markup'}
fit <- lm (mpg ~ cyl+hp+wt, data = mtcars)
fit
```

---
## Analyzing residuals
```{r plot, results='markup', fig.height=4.5, fig.width=13.5}
par(mfrow = c(1, 4))
plot(fit)
```

---
## Making predictions
Let's try a 6-cylinder vehicle with average horsepower and weight:
```{r p1, results='asis'}
v1 <- data.frame(cyl=c(6), hp=c(146.7), wt=c(3.217)); ans <- predict(fit, newdata=v1); ans[[1]]
```

Then, a 4-cylinder vehicle with mininal horsepower and weight:
```{r p2, results='asis'}
v2 <- data.frame(cyl=c(4), hp=c(52), wt=c(1.513)); ans <- predict(fit, newdata=v2); ans[[1]]
```

Finally, a 8-cylinder vehicle with maximun horsepower and weight:
```{r p3, results='asis'}
v3 <- data.frame(cyl=c(8), hp=c(335), wt=c(5.424)); ans <- predict(fit, newdata=v3); ans[[1]]
```